Model-Based and Model-Free Reinforcement Learning in Accelerator Operation with Application to FERMI FEL

### 2020-12-09 main.tex
- papers change

\newcommand{\NB}[1]{\textcolor{red}{#1}}
\include{tex/defs}

@@

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. Achieving this demands to consider several control problems simultaneously \cite{Kain2020}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015,Albright2019} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance.\\
	 Recently, the community has begun to explore a novel approach to solve control problems. Reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems is possible.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller - the sample-efficiency, since RL methods are known to be data-hungry \cite{Sutton2018,DulacArnold2019}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at Elettra Sincrotrone Trieste.\\
	 Two different algorithm classes (\emph{NAF} and \emph{AE-DYNA}) were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample-complexity as in accelerator control problems are presented.
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results of the experiments 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

@@

	A free-electron laser is a fourth-generation light source where the lasing medium consists of a very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronisation with external timing systems.\\
	The external optical laser signal provides is a contribution to the FEL process in the modulator where it interacts with the relativistic electron beam modulating it in energy. The modulation in energy is converted into a charge modulation in the dispersive section, and finally, the density modulated beams radiation is amplified in the section of the radiator.\\
	 The importance of ensuring the best possible overlapping between the seed laser and the electron beam in the modulator is therefore evident.\\

@@

	The state $\bs$ is a four dimensional vector holding the current voltage values applied to the piezo motors, where each component lies the normalzed interval [-1, 1]. Two values correspond to the two DOF of each mirror. The action $\ba$ is four dimensional, namely a delta step on the voltages at time-step $t$ $\bs_t$:

@@

	The training is done in episodes with a uniformly\footnote{in the normalized state-space} randomized initial state and a specific maximal length of taken steps afterwards - the horizon. For reason discussed later, the horizon varies in the applications between either 10 or 50 steps. An early termination happens if a specific threshold is obtained, which lies in all cases at 95\% of the maximal achievable intensity of the system.\\

@@

	Assume states $\bs$ the set of all states $\states$ and actions $\ba$ all actions $\actions$ and a reward function $\reward : \states \times \actions \rightarrow \real$, a scalar $\discount \in (0,1]$ called discount factor and an initial state distribution $\initstate$. $\transitions(\bs_{t+1}|\bs_t,\ba_t)$ characterises the probability to end in a state $\bs_{t+1}$ if an action $\ba_t$ is taken at state $\bs_t$. The tuple \mbox{$\mdp = (\states,\actions,\transitions,\initstate,\reward,\discount)$} defines a Markov decision process.\\

@@

	We focus on the main principles of MBRL. An overview can be found e.g. in \cite{Sutton2018,Levine2020}. In the following, we discuss the normalised advantage function (\emph{NAF}) algorithm in some detail, as it has good characteristics for accelerator control problems \cite{Kain2020,Hirlaender2020a}.

@@

		Q^\policy(\bs_t,\ba_t) := \mathbb E_{\traj \sim p_{\policy}(\traj|\bs_t,\ba_t)}\left[\sum_{t=t'}^{\horizon}\discount^{(t'-t)} r(\bs_t,\ba_t)\right],

@@

	is expressed as $Q^\policy_\theta(\bs,\ba)$, where $\theta$ denotes the parameters of the function approximator. By satisfying the Bellmann-optimality equation $Q^\policy_\theta$ can be trained towards the optimal $Q^*(\bs,\ba)$ by minimizing the Bellman error:

@@

		\policy_\theta(\bs)=(\delta(\ba)-\arg\!\max_\ba Q_\theta(\bs,\ba)).

@@

	\subsection{Uncertainty aware DYNA-style reinforcement learning}
	%The original DYNA algorithm \cite{Kurutach2018} is modified here in several aspects.

@@

The 'anchored ensembling' method, as treated in \cref{appendix:The impact of noise}, usually yields good results already with a small number of models. Empirical results showed that already three models were satisfactory to see definite improvements over a single network approach (see \cref{fig:Compare_models_sizes})). The main goal is not to determine the exact posterior probability of the model, but, as already mentioned, providing the uncertainty to not over-train the controller at areas without sufficient data.\\ A small densely connected two-layer network with around 15-25 nodes each and $tanh$ activation functions were used. The last layer was linear, and the inputs $\{\bs,\ba\}$ were normalised to the interval [-1,1].\\

@@

One of the most crucial points is how model uncertainties are taken into account by the MFRL controller. Several different approaches were tried. One way is to take the mean of the models $\mu_m$ and the standard deviation $\sigma_m$ and sample from $\gauss(\mu_m,\sigma_m)$. Another strategy is to randomly select a model to provide at each training step, which demonstrated the best performance the original implementation of the \emph{ME-TRPO} algorithm and was used in the experiments labelled \emph{ME-TRPO} \cite{Kurutach2018}. A pessimistic selection would only select the model resulting in the lowest predicted reward and showed constant but too slow improvement for our tests.
Good results were also obtained by following a randomly selected single model each full episode in combination with the soft-actor-critic (\emph{SAC}) \cite{fujimoto2018addressing,Hill2018}, and were used in the experiments labelled \emph{AE-DYNA SAC}. \\

@@

To decide which MFRL algorithm to use, two main algorithm classes have to be considered: the on and the off-policy algorithms. The online algorithm shows a more stable convergence in general, while off-policy algorithms have the advantage that the data buffer can be filled with real data. An attractive off-policy algorithm is \emph{SAC}. The \emph{SAC} not only tries to maximise $J$ \cref{eq:cumulative_reward} but also simultaneously is regularised to maximise the entropy in the action space. In this way, exploration is encouraged to avoid getting stuck in a local optimum and has a good trade-off between exploration and exploitation.\\

@@

	\subsubsection{Overview of the used algorithms}
	\Cref{tab:overview_algorithms} shows a comparison of the discussed algorithms. Details are provided in the appendix. All algorithms are suitable for many control tasks as common in accelerator operation. Their strength lies in the high sample-efficiency, but they differ in representational power and noise robustness. \\
	In \cref{sec:Experimental results from FERMI RL online tests} the \emph{NAF2},
	\emph{ME-TRPO} and \emph{AE-DYNA} are tested and compared on the real environment.
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
	\caption{\label{tab:overview_algorithms}%
		An overview of the algorithms discussed in this paper.
	}
	\begin{ruledtabular}
		\begin{tabular}{lllll}
			\textrm{Algorithm}&
			\textrm{Class}&
			\textrm{ \begin{tabular}{@{}c@{}}Noise\\robustness\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Represent.\\power\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Sample\\efficiency\end{tabular}}\\
			\colrule
			\emph{NAF} & MFRL & low &low &high\\
			\emph{NAF2} &MFRL & high &low& high\\
			\emph{ME-TRPO} & MBRL & low& high& high\\
			\emph{AE-DYNA} & MBRL & high& high& high\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

@@

	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_convergence.pdf}
		\caption{The training metrics of the \emph{AE-DYNA-SAC} on the FERMI FEL using a single network (dashed) and a double network (solid). The Bellman error (\cref{eq:minimize_bellmann_optimality}) and the state-value function (\cref{eq:state-value-function}) are shown. }
		\label{fig:NAF_convergence}
	\end{figure}
	In total, four tests were carried out, two using a single network and two using the double network architecture. A motivation for the used algorithmic set-up is given in \cref{appendix:naf2} on a classical example from control theory, the \emph{inverted pendulum}. In \cref{fig:comparsion_noise} the role \emph{smoothing} to increase the noise robustness can be seen. Therefore \emph{smoothing} was applied in all experiments.\\
	\Cref{fig:NAF_training} displays the results, averaged over the two tests. A training of 100 episodes was accomplished. In the upper figure, the number of iterations per episode is plotted, including the cumulative number of steps. The green line in the lower plot of \cref{fig:NAF_training} indicates the 95\% intensity reward threshold, to accept an episode to be successfully finished.
	In the verification of 50 episodes (\cref{fig:NAF_verification}) both algorithms show similar performance, while the double network needed less training steps, and reveals a more stable overall performance. \\
	Additionally, the convergence metrics of the two algorithms is plotted in \cref{fig:NAF_convergence} against the number of training steps. The blue curves show the Bellmann error \cref{eq:minimize_bellmann_optimality}, which is comparable in both cases. The state-value function $V$ (\cref{eq:state-value-function}), which is a direct output of the neural net (\cref{eq:state-action-value-approxiation}), converges to a reasonable value for the double network within the shown 700 steps, whereas the single network seems to overestimate the value. In the single-network case, convergence is reached after around 1400 steps. In the plot $V$ was averaged over 200 states.
	\subsection{MBRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/AE-DYNA_observables.pdf}
		\caption{The training of the \emph{AE-DYNA-SAC} on the FERMI FEL.}
		\label{fig:AE-DYNA_observables}
	\end{figure}

@@

	The second test campaign was employing the \emph{AE-DYNA} algorithm, as a representative for pure MBRL algorithms. Two variants were implemented: the \emph{ME-TRPO} variant and the \emph{AE-DYNA SAC} variant. The algorithmic design details are discussed in \cref{ss:critical_design}. 

@@

	Secondly, the \emph{AE-DYNA SAC} was tested, which uses the \emph{SAC}- algorithm \cite{Haarnoja2018a}. In this test, the controller is reset each time, when new data for the dynamics model training is acquired. Consequently, the performance drops each time the dynamics model is retrained, as shown in \cref{fig:AE-DYNA_observables}.\\

>>>>

\newcommand{\NB}[1]{\textcolor{red}{#1}}
\newcommand{\tocheck}[1]{\textcolor{blue}{#1}}
\include{tex/defs}

@@

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. Achieving this demands to consider several control problems simultaneously \cite{Kain2020,Scheinker2018}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015,Albright2019} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance.\\
	 Recently, the community has begun to explore a novel approach to solve control problems. Reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems is possible.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller - the sample-efficiency, since RL methods are known to be data-hungry \cite{Sutton2018,DulacArnold2019}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at \emph{Elettra Sincrotrone Trieste}.\\
	 Two different algorithm classes, a modification of the normalized advantage function \emph{NAF} (\cref{ss:Normalized advantage function}) and a novel anchored ensembling model-based algorithm, the \emph{AE-DYNA} (\cref{ss:Uncertainty aware DYNA-style reinforcement learning}), were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample-complexity as in accelerator control problems are presented.
	 \subsection{An Overview of the Main Results}
	 We demonstrate optimization techniques that simultaneously adjust 4 parameters, the tilt and incline of 2 mirrors that control the trajectory and overlap of the seed laser in the FERMI FEL relative to the beam in the undulator. We show that our algorithms require at most 1000 training sets, after which they are able to maximize the FERMI FEL’s output intensity to > that 95\% of the maximum within only ~3 to ~5 steps depending on which algorithm is used. Also we show the operational applicability of purely model-based reinforcement learning in a accelerator control problem.\\
	  Furthermore, our algorithms can perform real-time learning based on data and therefore can be re-run and re-trained for time-varying systems (is this true?).
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results of the experiments 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

@@

	A free-electron laser is a fourth-generation light source where the lasing medium consists of a very-high-speed electron moving freely through a magnetic structure. By using an external seeding source, the FERMI FEL has several advantages relative to standard FEL approaches in terms of increased stability in pulse and photon energy, reduced size, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronization with external timing systems.\\
The external optical laser signal interacts with the relativistic electron beam in the undulator, introducing an energy modulation that aids in the FEL process. The modulation in energy is converted into a charge modulation in the dispersive section, and finally, the density modulated beams radiation is amplified in the section of the radiator.\\
	 The importance of ensuring the best possible overlap between the seed laser and the electron beam in the modulator is therefore evident.\\

@@

	The state $\bs$ is a four dimensional vector holding the current voltage values applied to the piezo motors, where each component lies within the normalized interval [-1, 1]. Two values correspond to the two DOF of each mirror. The action $\ba$ is four dimensional, namely a delta step on the voltages at time-step $t$ $\bs_t$:

@@

	The training is done in episodes with a uniformly\footnote{in the normalized state-space} randomized initial state and a specific maximal length of taken steps afterwards - the horizon. For reason discussed later, the horizon varies in the applications between either 10 or 50 steps. An early termination happens if a specific threshold is obtained, which lies in all cases at 95\% of the maximal achievable intensity of the system \tocheck{discussion with Niky}.\\

@@

	In what follows, we denote the set of all states $\bs$ by $\states$ and the set of all actions $\ba$ by $\actions$. Relative to state and action vectors, $(\bs,\ba)$, we define a reward function $\reward : \states \times \actions \rightarrow \real$, a scalar $\discount \in (0,1]$ called discount factor and an initial state distribution $\initstate$. $\transitions(\bs_{t+1}|\bs_t,\ba_t)$ characterises the probability to end in a state $\bs_{t+1}$ if an action $\ba_t$ is taken at state $\bs_t$. The tuple \mbox{$\mdp = (\states,\actions,\transitions,\initstate,\reward,\discount)$} defines a Markov decision process.\\

@@

	\tocheck{Why Q learning?}
	We focus on the main principles of MBRL. An overview can be found e.g. in \cite{Sutton2018,Levine2020}. In the following, we discuss the normalised advantage function (\emph{NAF}) algorithm in some detail, as it has good characteristics for accelerator control problems as its high sample efficiency\cite{Kain2020,Hirlaender2020a}.

@@

		Q^\policy(\bs_t,\ba_t) := \mathbb E_{\traj \sim p_{\policy}(\traj|\bs_t,\ba_t)}\left[\sum_{t=t'}^{\horizon}\discount^{(t'-t)} r(\bs_t,\ba_t)\right].

@@

	is expressed as $Q^\policy_\theta(\bs,\ba)$, where $\theta$ denotes the parameters of the function approximator, such as the weights of a neural network. By satisfying the Bellmann-optimality equation $Q^\policy_\theta$ can be trained towards the optimal $Q^*(\bs,\ba)$ by minimizing the Bellman error:

@@

		\policy_\theta(\bs)=\delta(\ba-\arg\!\max_\ba Q_\theta(\bs,\ba)).

@@

	\subsection{Uncertainty aware DYNA-style reinforcement learning}\label{ss:Uncertainty aware DYNA-style reinforcement learning}
	%The original DYNA algorithm \cite{Kurutach2018} is modified here in several aspects.

@@

The 'anchored ensembling' method, as treated in \cref{appendix:The impact of noise}, usually yields good results already with a small number of models. Empirical results showed that already three models were satisfactory to see definite improvements over a single network approach (see \cref{fig:Compare_models_sizes}). The main goal is not to determine the exact posterior probability of the model, but, as already mentioned, providing the uncertainty to not over-train the controller at areas without sufficient data.\\
A small densely connected two-layer network with around 15-25 nodes each and $tanh$ activation functions were used. The last layer was linear, and the inputs $\{\bs,\ba\}$ were normalised to the interval [-1,1].\\

@@

One of the most crucial points is how model uncertainties are taken into account by the MFRL controller. Several different approaches were tried. One way is to take the mean of the models $\mu_m$ and the standard deviation $\sigma_m$ and sample from $\gauss(\mu_m,\sigma_m)$. Another strategy is to randomly select a model to provide at each training step, which demonstrated the best performance the original implementation of the \emph{ME-TRPO} algorithm and was used in the experiments labelled \emph{ME-TRPO} \cite{Kurutach2018}. A pessimistic selection would only select the model resulting in the lowest predicted reward and showed constant but too slow improvement for our online-training.
Good results were also obtained by following a randomly selected single model each full episode in combination with the soft-actor-critic (\emph{SAC}) \cite{fujimoto2018addressing,Hill2018}, and were used in the experiments labelled \emph{AE-DYNA-SAC}. \\

@@

To decide which MFRL algorithm to use, two main algorithm classes have to be considered: the on and the off-policy algorithms. The online algorithm shows a more stable convergence in general, while off-policy algorithms have the advantage that the data buffer can be filled with real data. An attractive off-policy algorithm is \emph{SAC}. The \emph{SAC} not only tries to maximise $J$ \cref{eq:cumulative_reward} but also simultaneously is regularised to maximise the entropy in the action space \cite{Haarnoja2018a}. In this way, exploration is encouraged to avoid getting stuck in a local optimum and has a good trade-off between exploration and exploitation.\\

@@

	\subsubsection{Overview of the used algorithms}
	\Cref{tab:overview_algorithms} shows a comparison of the discussed algorithms. Details are provided in the appendix. All algorithms are suitable for many control tasks as common in accelerator operation. Their strength lies in the high sample-efficiency, but they differ in representational power and noise robustness. \\
	In \cref{sec:Experimental results from FERMI RL online tests} the \emph{NAF2},
	\emph{ME-TRPO} and \emph{AE-DYNA} are tested and compared on the real environment.
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
	\caption{\label{tab:overview_algorithms}%
		Overview of the algorithms.
	}
	\begin{ruledtabular}
		\begin{tabular}{lllll}
			\textrm{Algorithm}&
			\textrm{Class}&
			\textrm{ \begin{tabular}{@{}c@{}}Noise\\robustness\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Represent.\\power\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Sample\\efficiency\end{tabular}}\\
			\colrule
			\emph{NAF} & MFRL & low &low &high\\
			\emph{NAF2} &MFRL & high &low& high\\
			\emph{ME-TRPO} & MBRL & low& high& high\\
			\emph{AE-DYNA} & MBRL & high& high& high\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

@@

	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_convergence.pdf}
		\caption{The training metrics of the \emph{AE-DYNA-SAC} on the FERMI FEL using a single network (dashed) and a double network (solid). The Bellman error (\cref{eq:minimize_bellmann_optimality}) and the state-value function (\cref{eq:state-value-function}) are shown. }
		\label{fig:NAF_convergence}
	\end{figure}
	In total, four tests were carried out, two using a single network and two using the double network architecture. A motivation for the used algorithmic set-up is given in \cref{appendix:naf2} on a classical example from control theory, the \emph{inverted pendulum}. In \cref{fig:comparsion_noise} the role \emph{smoothing} to increase the noise robustness can be seen. Therefore \emph{smoothing} was applied in all experiments.\\
	\Cref{fig:NAF_training} displays the results, averaged over the two tests \footnote{Considering the training is stochastic with random initial conditions, by chance, the training of the double network variant started above the threshold in both cases.}. A training of 100 episodes was accomplished. In the upper figure, the number of iterations per episode is plotted, including the cumulative number of steps. The green lines in the lower plot of \cref{fig:NAF_training} indicate the 95\% intensity reward threshold, to accept an episode to be successfully finished. The blue lines show the cumulative reward during the epoch.
	In the verification of 50 episodes (\cref{fig:NAF_verification}) both algorithms show similar performance, while the double network needed less training steps, and reveals a more stable overall performance. \\
	Additionally, the convergence metrics of the two algorithms is plotted in \cref{fig:NAF_convergence} against the number of training steps. The blue curves show the Bellmann error \cref{eq:minimize_bellmann_optimality}, which is comparable in both cases. The state-value function $V$ (\cref{eq:state-value-function}), which is a direct output of the neural net (\cref{eq:state-action-value-approxiation}), converges to a reasonable value for the double network within the shown 700 steps, whereas the single network seems to overestimate the value. In the single-network case, convergence is reached after around 1400 steps. In the plot $V$ was averaged over 200 randomly selected states.
	\subsection{MBRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/AE-DYNA_observables.pdf}
		\caption{The training of the \emph{AE-DYNA-SAC} on the FERMI FEL.}
		\label{fig:AE-DYNA_observables}
	\end{figure}

@@

	The second test campaign was employing the \emph{AE-DYNA} algorithm, as a representative for pure MBRL algorithms. Two variants were implemented: the \emph{ME-TRPO} variant and the \emph{AE-DYNA-SAC} variant. The algorithmic design details are discussed in \cref{ss:critical_design}. 

@@

	Secondly, the \emph{AE-DYNA-SAC} was tested, which uses the \emph{SAC}- algorithm \cite{Haarnoja2018a}. In this test, the controller is reset each time, when new data for the dynamics model training is acquired. Consequently, the performance drops each time the dynamics model is retrained, as shown in \cref{fig:AE-DYNA_observables}.\\
